Making Sequential Programs Deterministic

### 2019-04-03 randoop-case-study.tex
Explain the large number of `@Det` annotations

>>>>

The large number of \<@Det> annotations has two main reasons.

One is that we annotated some core components of Randoop to require all
boolean expressions used in conditionals to be deterministic.  (This is an
option in our implementation, which increases soundness.)  This forced
their clients, and much of the Randoop codebase, to be deterministic.
These annotations are not incorrect, but they are stricter than necessary
because some types could otherwise be @PolyDet, which is the default for
formal parameter and return types.  We plan to re-do the annotation effort
from scratch, and the number of annotations will be much lower.

The second reason is a limitation in \theDeterminismCheckerImplementation.
\TheDeterminismChecker does not support qualifier polymorphism over
classes.  This means that fields must be deterministic.  Our annotations in
Randoop use qualifier polymorphism extensively on methods but cannot use it
on classes, and this leads to many more Det annotations than would be
needed otherwise.
